Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-15 paper/main.tex
Standardize on audio-description (AD) not audio-only (AO)
You actually introduce it as such, and I think this is a much better
term that makes clear that this is a narrative, and not just the sound
track of the movie.

% Open research question
In this study, we investigate if increased hemodynamic activity in the PPA
correlates with ``spatial information'' presented under more ecologically valid
conditions.
% we are different We used two naturalistic
Therefore, we annotated perceptual information embedded in two [perceptual]
rich/multidimensional and continuous naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews):
% audio-description
a) the audio-description of the Hollywood movie ``Forrest Gump'' (i.e. the
audio-only variant of the movie), and
% audio-visual
b) the [actual] audio-visual movie [itself].
% studyforrest dataset
We then analyzed corresponding fMRI data from the same subjects that listened
to the audio-description and watched the audio-visual movie as part of the
publicly available studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org}).
% first: group level AO
First on a group average level, general linear model (GLM) contrasts based on
the audio-description's annotation are used to test if spatial information
embedded in an exclusively auditory stimulus correlates with increased
hemodynamic activity in the PPA that we defined using a block-designed visual
localizer experiment done with the same subjects \citep{sengupta2016extension}.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to GLM results based on the annotation of the movie.
% individual results
Lastly on the level of individual subjects and focussing on the
audio-description [as a possible substitute for a visual localizer], we compare
results of the naturalistic stimuli to results of the visual localizer
\citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract, intro to
discussion and conclusion} Our results demonstrate that (a), (b), (c).

@@

% intro
We used three subdatasets of the publicly available studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org}) that has already been
used by other research groups for independent research questions
(e.g. \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'',
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), and
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}).
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

\subsection{Participants}
% AO study
In the AO study \citep{hanke2014audiomovie}, 20 German native speakers (all
right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie}.
% AV study
In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female) of the prior AO study watched the audio-visual movie
with dubbed German audio track \citep{ForrestGumpDVD}.
% VIS study
In the VIS study \citep{sengupta2016extension}, the same 15 participants took
part in a six-category block-design visual localizer.

@@

% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description that was
broadcast as an additional audio track for visually impaired listeners on Swiss
public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AO: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}).
% procedure: questionnaire
Subjects filled out a questionnaire on their basic demographic information
and familiarity with the movie.
% AO & AV: instructions
Before the experiment, participants were instructed to inhibit physical
movements except for eye-movements, and otherwise to simply ``enjoy the
audiobook'' or ``enjoy the movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

@@

% AO
In the AO study, visual instructions were presented on a rear-projection screen
inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.

@@

\todo[inline]{auditory stimulation was the same in AO and AV?}

% AO & AV: auditory stimulation
In the AO and AV study, auditory stimulation was delivered through an MR confon
mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB (Terratec)
sound card through an optical connection.

@@

% AO
In the AO study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
% auxiliary scans
Auxiliary scans for slice alignment and motion- and distortion-correction were
performed at the beginning of the first fMRI recording session and also after
the break at the start of the recording for the second half of the movie.
% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order.
% slice positioning
Philips' ``SmartExam'' was used to automatically position slices in AC-PC
orientation such that the topmost slice was located at the superior edge of the
brain. This automatic slice positioning procedure was identical in the AV and
VIS study, and yielded a congruent geometry across paradigms.
% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
volumes for segment 1–8).

@@

\todo[inline]{what is missing: As I see it, AO must have been downsampled to
2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series of those 15 participants in the studyforrest dataset that took
part in all three experiments were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data were already corrected for motion and aligned by non-linear warping to a
participant-specific BOLD template image \citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant were dropped to due to invalid distortion correction
during scanning of the AO stimulus.
% preprocessing intro
All further analysis steps of the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% AO annotation
For the analysis of the AO stumulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
a] disco'', ``[the platoon wades through a] rice field''). They also comprise
words that could count as a member of another categories in case the narrator
uses these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').

@@

% AO regressors

@@

        analysis of the audio-only (AO) stimulus. Some of the annotation's

@@

% pooling of categories
To create the regressor for the GLM of the AO stimulus, some of
the original 18 categories that were similar but offered only a small amount of
counts were pooled resulting in eleven new categories [that served as
experimental conditionso] (see Table \ref{tab:ao-events}).
% handling of se_new and se_old
Moreover, events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``[a] physician'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.

@@

% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AO stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms?"; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same; it is rephrased now though}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.
% convolving
Events for all regressors of the AV stimulus were convolved with a
double gamma hemodynamic response function (HRF).

@@

se\_new & control for AO narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII

@@

se\_old & control for AO narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII

@@

% irrespectible of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).
% AV COPEs: intro
The rationale that this approach would still yield categories correlating with
increased hemodynamic activity in the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal, grill2006repetition}.
% null regressor
As for the regressors for AO stimulus, a null regressor was chosen for a
regressor in a segment if that segment did not contain an event of the
corresponding category.
% no cut condition: intro
A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
created as a control condition to create negative control contrasts:
% procedure
Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
a minimum distance of \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe
jetzt lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AO und
AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das
bedeutet); COH: what is better: reference to table as it is now (more precise,
but harder to read) or use non-cryptic words in the figure?}

@@

% intro
To test the robustness our approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in event counts.
% thus: primary contrasts
We chose one ``primary contrast'' for every stimulus before running the
analyses.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.\todo{oh, lord!}

% AO: primary contrast
In the primary contrast of the AO stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all non-geometry related categories (\texttt{body},
\texttt{bodypart}, \texttt{fahead}, \texttt{object}, \texttt{sex\_f},
\texttt{sex\_m}) except \texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

>>>>

% Open research question
In this study, we investigate if increased hemodynamic activity in the PPA
correlates with ``spatial information'' presented under more ecologically valid
conditions.
% we are different We used two naturalistic
Therefore, we annotated perceptual information embedded in two [perceptual]
rich/multidimensional and continuous naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews):
% audio-description
a) the audio-description (AD) of the Hollywood movie ``Forrest Gump'',
and
% audio-visual
b) the original audio-visual (AV) movie.
% studyforrest dataset
We then analyzed corresponding fMRI data from the same subjects that listened
to the audio-description and watched the audio-visual movie as part of the
publicly available studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org}).
% first: group level AD
First on a group average level, general linear model (GLM) contrasts based on
the audio-description's annotation are used to test if spatial information
embedded in an exclusively auditory stimulus correlates with increased
hemodynamic activity in the PPA that we defined using a block-designed visual
localizer experiment done with the same subjects \citep{sengupta2016extension}.
% second: group level AV
Second as conceptual/cross-modal control, we compare results of the
audio-description to GLM results based on the annotation of the movie.
% individual results
Lastly on the level of individual subjects and focussing on the
audio-description [as a possible substitute for a visual localizer], we compare
results of the naturalistic stimuli to results of the visual localizer
\citep{sengupta2016extension}.
% results
\todo[inline]{following paragraph will be similar to abstract, intro to
discussion and conclusion} Our results demonstrate that (a), (b), (c).

@@

% intro
We used three subdatasets of the publicly available studyforrest dataset
(\href{http://www.studyforrest.org}{studyforrest.org}) that has already been
used by other research groups for independent research questions
(e.g. \citep{ben2018hippocampal, jiahui2019predicting, hu2017decoding,
lettieri2019emotionotopy, nguyen2016integration}).
% used studies
The same subjects were
% AD
a) listening to the audio-description (AD study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'',
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), and
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}).
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

\subsection{Participants}
% AD study
In the AD study \citep{hanke2014audiomovie}, 20 German native speakers (all
right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie}.
% AV study
In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female) of the prior AD study watched the audio-visual movie
with dubbed German audio track \citep{ForrestGumpDVD}.
% VIS study
In the VIS study \citep{sengupta2016extension}, the same 15 participants took
part in a six-category block-design visual localizer.

@@

% AD & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description that was
broadcast as an additional audio track for visually impaired listeners on Swiss
public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AD: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

% AD & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}).
% procedure: questionnaire
Subjects filled out a questionnaire on their basic demographic information
and familiarity with the movie.
% AD & AV: instructions
Before the experiment, participants were instructed to inhibit physical
movements except for eye-movements, and otherwise to simply ``enjoy the
audiobook'' or ``enjoy the movie'' respectively.
% AD & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

@@

% AD
In the AD study, visual instructions were presented on a rear-projection screen
inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.

@@

\todo[inline]{auditory stimulation was the same in AD and AV?}

% AD & AV: auditory stimulation
In the AD and AV study, auditory stimulation was delivered through an MR confon
mkII+ driving custom-built in-ear headphones (HP-M01, MR confon GmbH, Magdeburg,
Germany; \citep{baumgart1998electrodynamic}) that reduced the scanner noise by
at least \unit[20–30]{dB}. Headphones were fed from an Aureon 7.1 USB (Terratec)
sound card through an optical connection.

@@

% AD
In the AD study, a whole-body \unit[7]{Tesla} Siemens MAGNETOM magnetic
resonance scanner equipped with a local circularly polarized head transmit and a
32 channel brain receive coil (Nova Medical, Inc., Wilmington, MA, USA) acquired
T2*-weighted echo-planar images (gradient-echo, \unit[2]{s} repetition time
(TR), \unit[22]{ms} echo time, \unit[0.78]{ms} echo spacing, \unit[1488]{Hz/Px}
bandwidth, generalized autocalibrating partially parallel acquisition,
acceleration factor 3, \unit[2]{Hz/Px} bandwidth in phase encoding direction).
% slices
36 axial slices (thickness \unit[1.4]{mm}, \unit[1.4 $\times$ 1.4]{mm} in-plane
resolution, \unit[224]{mm} field-of-view, anterior-to-posterior phase encoding
direction) with a \unit[10]{\%} inter-slice gap were recorded in ascending
order.
% slice orientation
Slices were oriented to include the ventral portions of frontal and occipital
cortex while minimizing intersection with the eyeballs.
% FOV
The field of view was centered on the approximate location of Heschl's gyrus.
% motion correction
EPI images were online-corrected for motion and geometric distortions [+++Oh, S.
et al. 2012; In, M. \& Speck, O., 2012; Chung, J. et al., 2011+++]
% auxiliary scans
Auxiliary scans for slice alignment and motion- and distortion-correction were
performed at the beginning of the first fMRI recording session and also after
the break at the start of the recording for the second half of the movie.
% AV & VIS
In the AV and VIS study, a whole-body \unit[3]{Tesla} Philips Achieva dStream
MRI scanner equipped with a 32 channel head coil acquired T2*-weighted
echo-planar images (gradient-echo, \unit[2]{s} repetition time, \unit[30]{ms}
echo time, \unit[90]{$^{\circ}$} flip angle, \unit[1943]{Hz/Px} bandwidth,
parallel acquisition with sensitivity encoding (SENSE) reduction factor 2).
% slices
35 axial slices (thickness \unit[3.0]{mm}, \unit[10]{\%} inter-slice gap) with
\unit[80 $\times$ 80]{voxels} (\unit[3.0 $\times$ 3.0]{mm} of in-plane
resolution, \unit[240]{mm} field-of-view) and an anterior-to-posterior phase
encoding direction were recorded in ascending order.
% slice positioning
Philips' ``SmartExam'' was used to automatically position slices in AC-PC
orientation such that the topmost slice was located at the superior edge of the
brain. This automatic slice positioning procedure was identical in the AV and
VIS study, and yielded a congruent geometry across paradigms.
% no. of volumes
A total of 3599 volumes were recorded for each participant in each of the
naturalistic stimulus paradigms (451, 441, 438, 488, 462, 439, 542, and 338
volumes for segment 1–8).

@@

\todo[inline]{what is missing: As I see it, AD must have been downsampled to
2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series of those 15 participants in the studyforrest dataset that took
part in all three experiments were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data were already corrected for motion and aligned by non-linear warping to a
participant-specific BOLD template image \citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant were dropped to due to invalid distortion correction
during scanning of the AD stimulus.
% preprocessing intro
All further analysis steps of the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

@@

% AD annotation
For the analysis of the AD stumulus, we extended a publicly available annotation
of speech \citep{haeusler2020speechanno} by further annotating words spoken by
the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content based on a set of rules.
% reference to table with rules and examples
A complete overview of all 18 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% why and how of categories 1
Some categories reflect the verbal counterpart of the stimulus categories that
were used in the visual localizer experiment (e.g. \texttt{body}, \texttt{face},
\texttt{head}, \texttt{object}, \texttt{setting\_new}, and
\texttt{setting\_rec}).
% why and how of categories 2
Other categories were created to semantically cluster remaining nouns into
categories that had no counterpart in the visual localizer experiment (e.g.
\texttt{bodypart}, \texttt{female}, \texttt{fname}, \texttt{furniture},
\texttt{geo}, \texttt{geo-room}, \texttt{male}, and \texttt{persons}).
% categories in detail
%Nouns were categorized by the verbal clue they provide about the
%cinematographic scene's environment (\texttt{geo}, \texttt{geo-room};
%\texttt{setting\_new}, \texttt{setting\_old}), its inherent persons (e.g.
%\texttt{female}, \texttt{male}, \texttt{persons}), a person's body or worn
%clothes (\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a
%scene's inherent objects (\texttt{object}, \texttt{furniture}).  problem with
%hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec} comprise
not just words that describe a setting as a whole (e.g. ``[in] Greenbow'', ``[in
a] disco'', ``[the platoon wades through a] rice field''). They also comprise
words that could count as a member of another categories in case the narrator
uses these words to indicate a switch from one setting to another (e.g. ``[a]
physician'').

@@

% AD regressors

@@

        analysis of the audio-only (AD) stimulus. Some of the annotation's

@@

% pooling of categories
To create the regressor for the GLM of the AD stimulus, some of
the original 18 categories that were similar but offered only a small amount of
counts were pooled resulting in eleven new categories [that served as
experimental conditionso] (see Table \ref{tab:ao-events}).
% handling of se_new and se_old
Moreover, events that fell into one of the two setting-related categories
(\texttt{se\_new} or \texttt{se\_old}) but also into another category were
treated as belonging to the setting-related category (e.g. ``[a] physician'').
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.

@@

% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AD stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms?"; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same; it is rephrased now though}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.
% convolving
Events for all regressors of the AV stimulus were convolved with a
double gamma hemodynamic response function (HRF).

@@

se\_new & control for AD narrator & \aoSenewAll & \aoSenewI & \aoSenewII & \aoSenewIII & \aoSenewIV & \aoSenewV & \aoSenewVI & \aoSenewVII & \aoSenewVIII

@@

se\_old & control for AD narrator & \aoSeoldAll & \aoSeoldI & \aoSeoldII & \aoSeoldIII & \aoSeoldIV & \aoSeoldV & \aoSeoldVI & \aoSeoldVII & \aoSeoldVIII

@@

% irrespectible of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).
% AV COPEs: intro
The rationale that this approach would still yield categories correlating with
increased hemodynamic activity in the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal, grill2006repetition}.
% null regressor
As for the regressors for AD stimulus, a null regressor was chosen for a
regressor in a segment if that segment did not contain an event of the
corresponding category.
% no cut condition: intro
A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
created as a control condition to create negative control contrasts:
% procedure
Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
a minimum distance of \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe
jetzt lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AD und
AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das
bedeutet); COH: what is better: reference to table as it is now (more precise,
but harder to read) or use non-cryptic words in the figure?}

@@

% intro
To test the robustness our approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in event counts.
% thus: primary contrasts
We chose one ``primary contrast'' for every stimulus before running the
analyses.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.\todo{oh, lord!}

% AD: primary contrast
In the primary contrast of the AD stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all non-geometry related categories (\texttt{body},
\texttt{bodypart}, \texttt{fahead}, \texttt{object}, \texttt{sex\_f},
\texttt{sex\_m}) except \texttt{furniture}.
% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.
